An algorithmic framework for generating contour parallel toolpaths with adaptive extrusion width for additive manufacturing

### 2019-08-27 4_method.tex
Updates from Overleaf

\subsection{Peripheral Beading}\label{sec_peripheral_height_adjustment}

@@

\paragraph{Beading} 
We associate each central node $v$ with a set of radial distances for each bead along with the width of that bead, which we call the \emph{beading} $B$.
For our distributed beading scheme we define the beading for a central node $v$ as:
\begin{align*}
    B &= \left\{ \left( w_0 , l_0 \right), \dots, \left( w_{n-1}, l_{n-1} \right) \right\} \\
    w_i &= 2R(v) / n  \\
    l_i &= 2R(v) / n (i + \nicefrac12)
\end{align*}
where
$w_i$ and $l_i$ are the width and location of the $i$th bead,
respectively, counting from the outline inward.
An example beading is visualized in the top of \cref{beading_interpolation}:
$B^V$ cover the total horizontal distance $d$ using $n=4$ beads all with the same width and radial locations $l$ evenly divided over the length $d$.

>>>>

\subsection{Beading}\label{sec_peripheral_height_adjustment}

@@

\paragraph{Beading} 
For toolpath geneWe associate each central node $v$ with a set of radial distances for each bead along with the width of that bead, which we call the \emph{beading} $B$.
For our distributed beading scheme we define the beading for a central node $v$ as:
\begin{align*}
    B &= \left\{ \left( w_0 , l_0 \right), \dots, \left( w_{n-1}, l_{n-1} \right) \right\} \\
    w_i &= 2R(v) / n  & \text{for all $i$}\\
    l_i &= 2R(v) / n (i + \nicefrac12) & \text{for all $i$}
\end{align*}
where
$w_i$ and $l_i$ are the width and location of the $i$th bead,
respectively, counting from the outline inward.
An example beading is visualized in the top of \cref{beading_interpolation}:
$B^V$ cover the total horizontal distance $d$ using $n=4$ beads all with the same width and radial locations $l$ evenly divided over the length $d$.
